\bf Model Visualization Techniques for a Social Network Model

### 2017-07-28 paper.Rnw
uncomment all the \hh stuff that i commented out previously and start a conversation.

\section{Introduction} 
% \st{
% \begin{itemize}
% %\item What? - model visualization and SAOMs. briefly dsecribe what these things are
% %\item Why? - bring light to the RSiena blackbox. Need ways to visualize network models, collections of networks. 
% \item How?
% \end{itemize}
% %also talk about other dynamic network models briefly to put SAOMs in context.
% }
%\hh{XXX - talk a bit about social networks first, why we want to model them, and that usually the models are not dynamic.}

Social networks have been studied for decades, beginning with a few foundational works, the most well known of which is the 1967 study, "The Small World Problem" by Stanley Milgram \citep{goldenberg09}. Examples of social networks include collaboration networks between academic researchers, friendship networks in a school or university, and trade networks between nations. In recent years, the study of social networks has grown in popularity due to an increase in the availability and access to social network data. There are many kinds of social networks, but there are not as many statistical models for social network data. Some network models that have been applied to social networks include the exponential random graph model and latent space models. These models, however, are only for single instance networks. If we only care about one network observation, that is not a problem, but if we have many observations of social network over time, these models may not be appropriate. When studying a network over time, which is referred to as a \textit{dynamic network}, we need a model that can take time into account. 
Models for dynamic social networks are extremely important because of how realistic they are. Social networks do not form spontaneously; they evolve over time. Ties are added and removed, and new actors join the network. Modeling the underlying mechanisms that create network changes over time is very complex but also has the potential to uncover hidden truths.

@@

\st{
%\par In order to estimate the parameters of  SAOMs the software SIENA, and its \texttt{R} implementation \texttt{RSiena}, was developed \cite{RSiena}. This software marks a huge contribution to the field of social network analysis., and when we began working with it we were eager to understand how it works. HH: we are still interested in this.
%\hh{The next sentence is very vague - make it more specific: what aspect of SAOMs is not well understood? I think what you want is something like ``SAOMs are not very tractable analytically with traditional methods, e.g. likelihood functions turn into very complex objects because of the sheer number of parameters involved. Therefore, computationally more tractable solutions are used to fit estimators, in particular, SAOMs are fit using ... }
Unlike other network models, SAOMs are not very well understood. They are relatively new, especially compared to the classic exponential random graph models, and they are not very tractable analytically with traditional methods. Likelihood functions turn into very complex objects due to the dependency structure inherent in the data. Therefore, computationally more tractable solutions are used to fit estimators, in particular, % Traditional modeling steps, like determining the likelihood function, are very complex. Because of this, 
SAOMs are fit to data using a series of MCMC phases for finding method of moments estimators. Rather than treat SAOM fits and the fitting process as black boxes, we combine the principals of network visualization with those of model visualization as discussed in \citet{modelvis}. %Here, we explore RSiena and SAOMs with innovative network visualizations, both static and dynamic.
By bringing some light to the underlying methods and structures ``behind the scenes" of SAOMs, we help researchers working with the models better understand the implications and analysis of these models.
}

@@

Some layout algorithms were designed to mimic physical systems, drawing the graphs based on the ``forces" connecting them. The network's edges act as springs pushing and pulling the nodes in a lower dimensional (usually two-dimensional) space. %Other algorithms use properties of the network's adjaceny matrix in order to place the nodes. \hh{XXX how does the adjacency matrix feature here? The adjacency matrix is  a different mathematical representation of a network, but describes the same network as a node-link diagram.} 
Some commonly used layout algorithms, such as  the Kamada-Kawai layout \citep{kamadakawai} and the Fruchterman-Reingold layout \citep{fruchterman-reingold}, treat networks like physical systems. Other algorithms are based on multi-dimensional scaling, which relies on a defined distance matrix, or an eigen value, which depends on the eigenvalues of the network's adjacency matrix \citep{drawingalgs}. The node-link diagram for our toy network is shown in Figure~\ref{fig:toyplots}.

The second primary method for network visualization uses the adjacency matrix of the network. The adjaceny matrix of a network, $\mathbf{A}$, describes the edges of a network in matrix form. An entry $A_{ij}$ of $\mathbf{A}$, for two nodes $i\neq j$ in the network is defined as 
\[
  A_{ij} =
  \begin{cases}
                                   1 &  \text{if an edge exists} i\to j \\
                                   0 & otherwise
  \end{cases}
\]
In an undirected network, $A_{ij} = A_{ji}$, but in a directed graph this is only true if there is an edge from $i$ to $j$ and from $j$ to $i$. Thus, $\mathbf{A}$ is always symmetric for undirected networks, and is symmetric for directed networks only if every edge between two nodes is reciprocated.
%\hh{XXX what is an adjacency matrix? - explain at this point in mathematical terms} 
This type of visualization is also shown in Figure~\ref{fig:toyplots} for our toy example.  %\hh{XXX What is the exact logic here that Ghoniem used to come to the conclusion that edges in undirected graphs are over-represented? Why would directed graphs make that better? wouldn't that just add to the number of edges? } This, however, may actually be an advantage for \emph{directed} graphs, where exactly the correct number of edges is represented in a matrix visualization, but a node-link diagram may underrepresent the edge count with overlapping edges.

<<toyplots, fig.show='hold', fig.cap="On the left, a node-link diagram of our directed toy network, with nodes placed using the Kamada-Kawai algorithm. On the right, the adjacency matrix visualization for that same network.", out.width='.49\\linewidth'>>=
toynetdat <- fortify(as.edgedf(toynet$edges), toynet$nodes)
ggplot(data = toynetdat) + 
  geom_net(aes(from_id=from_id, to_id=to_id), labelon = T, size = 10, labelcolour = 'white', ecolour = 'black', vjust = .5, hjust = .5, arrowgap = .05, directed = T) +
  theme_net() + 
  labs(title = "Node-Link Diagram")

@@

@
% \hh{XXX Explain each of these visualizations and either comment on the differences in the visualizations (colors) or don't show them. }

Each type of visualization comes with its own advantages and disadvantages. Paths between nodes are easier to determine with node-link diagrams than with adjacency matrix visualizations. In node-link diagrams, node information can be incorporated into the visualization by coloring or changing the shape of the points representing the nodes. This is not necessarily possible in matrix representation, which is more focused on edges. Adjacency matrix visualization is particularly useful, however, when the network is very complex, dense, or large. Experimental studies have shown this to be true. For example, with seven basic perceptual tasks on networks, including things like node and edge count, adjacency matrix visualizations outperform node-link diagrams as the size and density of the network increases \citep{adjmatviz}. One drawback of the adjacency matrix visualization that \citeauthor{adjmatviz} found was that edges are overrepresented for undirected graphs, due to the symmetry of $\mathbf{A}$. There is not one correct way to visualize network information, and we will be using both of the methods throughout this paper.

@@

%\hh{mostly lit review plus a detailed description of the model and fitting process.}

@@

For the network $x$ and each actor $i$ in the network, the number of times that an actor $i$ gets to change its ties, $x_{ij}$, to other nodes $j \neq i$ in the network is dictated by a \emph{rate function} $\rho(x, \mathbf{z}, \boldsymbol{\alpha})$. For this paper, we assume a simple rate function, $\rho(x, \mathbf{z}, \boldsymbol{\alpha}) = \alpha_m$ that is constant for all actors between observations at time $t_m$ to $t_{m+1}$. %\hh{XXX that means that the function is essentially just a rate parameter, right?}
Other modelling scenarios allow this rate to be more flexible,  e.g.\ a function that depends on the time period of observation, some actor-level covariates or some actor-level network statistics. 
%\hh{How is the rate parameter different from a rate parameter?}
In our model with the simple rate function, the rate parameter determines how quickly actor $i$ gets an opportunity to change one of its ties, $x_{ij}$ in the time period from $t_{m}$ to $t_{m+1}$. The model also assumes that the actors $i$ are conditionally independent given their ties, $x_{i1}, \dots, x_{in}$ at the current network state. \st{Let $\tau_i(m)$ be the wait time until actor $i$ makes its next change.For any time point, $T$, where $t_{m} \leq T < t_{m+1}$, the waiting time to the next change opportunity by actor $i$ is exponentially distributed with expected value $\alpha_m^{-1}$. The conditional independence assumption is expressed in Equation~\ref{eq:c1}.

@@

\hh{XXX we tried to estimate the rate based on the simulations - you could include a histogram of the number of changes for the 1000 simulations in the viz part XXX}

@@

%\hh{shouldn't that be independence? - make the conditional independence assumption above a labelled formula (e.g. C1) and then call it here }
Because of the conditional independence assumptions in Equation~\ref{eq:c1}, we can consider the objective function for each node separately, since only one tie from one node is changing at a time. The objective function is then written as 
\begin{equation} \label{eq:of1}
f_i(\boldsymbol{\beta}, x) = \sum_k \beta_k s_{ik}(x, \mathbf{Z}),
\end{equation}

for $x \in \mathcal{X}$, the space of all possible directed networks with the $n$ nodes, and $\mathbf{Z}$ matrix of covariates. The vector $\boldsymbol{\beta}$ are the parameters of the model with corresponding network and covariate statistics, $s_{ik}(x, \mathbf{Z})$, for $k = 1,\dots, K$. \hh{XXX ego node isn't defined yet - the description of the charts would be a good place for it.} Given the ego node, $i$, there are $n$ possible steps for the actor $i$ to take: either one of all current ties $x_{ij} = 1$ will be destroyed, a new tie will be created, or no change will occur.

The parameters, $\boldsymbol{\beta}$, are attached to various actor-level network statistics, $s_{ik}(x)$. %\hh{'There are always' ... that seems to come from a Snijder paper? Re-phrase this to be less vague: In the current implementation of RSiena (snijder) a model has minimally two parameters...} 
According to \citet[p. 371]{snijders01}, there should be at least two parameters included in the model: $\beta_1$ for the outdegree of a node, and $\beta_2$ for the number of reciprocal ties held by a node \st{The inclusion of these effects has origin in the classical exponential random graph model (ERGM) for networks. The statistics corresponding to these effects are written in terms of the edge variables $x_{ij}$, for $i \neq j$.} In the \texttt{RSiena} software, there are over 80 possible parameters to add to the model. The formulas for the effects are provided in \citet{RSienamanual}. The parameters, $\beta_k$, in the model can be split up into two groups: first, the structural effects, whose estimation only depend on the structure of the network, like the outdegree and reciprocity parameters mentioned above. %\hh{XXX move the last colored section to the front of this paragraph. That sets up the structure nicely, e.g. `In determining the covariates of a SAOM, two sources of parameters are considered: ...} 
The second set of effects are referred to as the actor-level or covariate effects. These covariate effects also depend on the structure of the network, and are written in terms of the tie variables $x_{ij}$, but also in terms of the covariates, $\mathbf{Z}$. A table of some possible structural and covariate effects is given in Table~\ref{tab:effects}. For a complete list of the network and covariate statistics that can currently be included in the objective function, see \citet{RSienamanual}.

@@

Using the distribution given in Equation~\ref{dist1} with mean $\mu = 0$ and scale $\sigma = 1$ as \citet{modelsSnijders} suggests %\hh{XXX I'm not following - which distribution do you mean by `this' distribution? The density above is the type 1 extreme value density. I got lost at the  ``objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$"} 
is convenient because it allows the probability the actor $i$ chooses to change its tie to actor $j$ in terms of the objective function alone. Let $p_{ij}(\boldsymbol{\beta}, x)$ be this probability. Next, write the network $x$ in its potential future state, where the tie $x_{ij}$ has changed to $1-x_{ij}$, as $x(i \leadsto j)$. Then, the probility that the tie $x_{ij}$ changes is

@@

\hh{This paragraph ends a bit abruptly - what is the future state probability used for?}

>>>>

\section{Introduction} 
% \st{
% \begin{itemize}
% %\item What? - model visualization and SAOMs. briefly dsecribe what these things are
% %\item Why? - bring light to the RSiena blackbox. Need ways to visualize network models, collections of networks. 
% \item How?
% \end{itemize}
% %also talk about other dynamic network models briefly to put SAOMs in context.
% }
\hh{XXX - talk a bit about social networks first, why we want to model them, and that usually the models are not dynamic.}
\st{XXX - okay, here is what i have done for that:
Social networks have been studied for decades, beginning with a few foundational works, the most well known of which is the 1967 study, "The Small World Problem" by Stanley Milgram \citep{goldenberg09}. Examples of social networks include collaboration networks between academic researchers, friendship networks in a school or university, and trade networks between nations. In recent years, the study of social networks has grown in popularity due to an increase in the availability and access to social network data. There are many kinds of social networks, but there are not as many statistical models for social network data.} Some network models that have been applied to social networks include the exponential random graph model and latent space models. These models, however, are only for single instance networks. If we only care about one network observation, that is not a problem, but if we have many observations of social network over time, these models may not be appropriate. When studying a network over time, which is referred to as a \textit{dynamic network}, we need a model that can take time into account. 
Models for dynamic social networks are extremely important because of how realistic they are. Social networks do not form spontaneously; they evolve over time. Ties are added and removed, and new actors join the network. Modeling the underlying mechanisms that create network changes over time is very complex but also has the potential to uncover hidden truths.

@@

\st{
%\par In order to estimate the parameters of  SAOMs the software SIENA, and its \texttt{R} implementation \texttt{RSiena}, was developed \cite{RSiena}. This software marks a huge contribution to the field of social network analysis., and when we began working with it we were eager to understand how it works. HH: we are still interested in this.
\hh{The next sentence is very vague - make it more specific: what aspect of SAOMs is not well understood? I think what you want is something like ``SAOMs are not very tractable analytically with traditional methods, e.g. likelihood functions turn into very complex objects because of the sheer number of parameters involved. Therefore, computationally more tractable solutions are used to fit estimators, in particular, SAOMs are fit using ... }
Unlike other network models, SAOMs are not very well understood. \st{They are relatively new, especially compared to the classic exponential random graph models, and they are not very tractable analytically with traditional methods. Likelihood functions turn into very complex objects due to the dependency structure inherent in the data. Therefore, computationally more tractable solutions are used to fit estimators, in particular, % Traditional modeling steps, like determining the likelihood function, are very complex. Because of this, 
SAOMs are fit to data using a series of MCMC phases for finding method of moments estimators.} Rather than treat SAOM fits and the fitting process as black boxes, we combine the principals of network visualization with those of model visualization as discussed in \citet{modelvis}. %Here, we explore RSiena and SAOMs with innovative network visualizations, both static and dynamic.
By bringing some light to the underlying methods and structures ``behind the scenes" of SAOMs, we help researchers working with the models better understand the implications and analysis of these models.
}

@@

Some layout algorithms were designed to mimic physical systems, drawing the graphs based on the ``forces" connecting them. The network's edges act as springs pushing and pulling the nodes in a lower dimensional (usually two-dimensional) space. %Other algorithms use properties of the network's adjaceny matrix in order to place the nodes. 
\hh{XXX how does the adjacency matrix feature here? The adjacency matrix is a different mathematical representation of a network, but describes the same network as a node-link diagram.} \st{XXX I'm taking this to mean I should describe adjacency matrices more, so I've added a discussion below. XXX }
Some commonly used layout algorithms, such as  the Kamada-Kawai layout \citep{kamadakawai} and the Fruchterman-Reingold layout \citep{fruchterman-reingold}, treat networks like physical systems. Other algorithms are based on multi-dimensional scaling, which relies on a defined distance matrix, or an eigen value, which depends on the eigenvalues of the network's adjacency matrix \citep{drawingalgs}. The node-link diagram for our toy network is shown in Figure~\ref{fig:toyplots}.

\st{The second primary method for network visualization uses the adjacency matrix of the network. The adjaceny matrix of a network, $\mathbf{A}$, describes the edges of a network in matrix form. An entry $A_{ij}$ of $\mathbf{A}$, for two nodes $i\neq j$ in the network is defined as 
\[
  A_{ij} =
  \begin{cases}
                                   1 &  \text{if an edge exists} i\to j \\
                                   0 & otherwise
  \end{cases}
\]
In an undirected network, $A_{ij} = A_{ji}$, but in a directed graph this is only true if there is an edge from $i$ to $j$ and from $j$ to $i$. Thus, $\mathbf{A}$ is always symmetric for undirected networks, and is symmetric for directed networks only if every edge between two nodes is reciprocated.}
\hh{XXX what is an adjacency matrix? - explain at this point in mathematical terms} \st{XXX see above XXX}
This type of visualization is also shown in Figure~\ref{fig:toyplots} for our toy example.  
<<toyplots, fig.show='hold', fig.cap="On the left, a node-link diagram of our directed toy network, with nodes placed using the Kamada-Kawai algorithm. On the right, the adjacency matrix visualization for that same network.", out.width='.49\\linewidth'>>=
toynetdat <- fortify(as.edgedf(toynet$edges), toynet$nodes)
ggplot(data = toynetdat) + 
  geom_net(aes(from_id=from_id, to_id=to_id), labelon = T, size = 10, labelcolour = 'white', ecolour = 'black', vjust = .5, hjust = .5, arrowgap = .05, directed = T) +
  theme_net() + 
  labs(title = "Node-Link Diagram")

@@

@
\hh{XXX Explain each of these visualizations and either comment on the differences in the visualizations (colors) or don't show them. }

Each type of visualization comes with its own advantages and disadvantages. Paths between nodes are easier to determine with node-link diagrams than with adjacency matrix visualizations. In node-link diagrams, node information can be incorporated into the visualization by coloring or changing the shape of the points representing the nodes. This is not necessarily possible in matrix representation, which is more focused on edges. Adjacency matrix visualization is particularly useful, however, when the network is very complex, dense, or large. Experimental studies have shown this to be true. For example, with seven basic perceptual tasks on networks, including things like node and edge count, adjacency matrix visualizations outperform node-link diagrams as the size and density of the network increases \citep{adjmatviz}. One drawback of the adjacency matrix visualization that \citeauthor{adjmatviz} found was that edges are overrepresented for undirected graphs, due to the symmetry of $\mathbf{A}$: the edge $x_{ij}$ for $i \neq j$ appears in $A$ twice: in $A_{ij}$ and $A_{ji}$.  \hh{XXX What is the exact logic here that Ghoniem used to come to the conclusion that edges in undirected graphs are over-represented? Why would directed graphs make that better? wouldn't that just add to the number of edges? } \st{XXX in undirected nets, the adj mat is symmetric, where one edge ($x_{ij}$) is represented in entry $i,j$ in the matrix and in entry $j,i$. So, there are many repetitions in the matrix, which makes the network appear more dense than it really is.} \st{This, however, may actually be an advantage for \emph{directed} graphs, where exactly the correct number of edges is represented in a matrix visualization, due to the fact that the edges $x_{ij}$ and $x_{ji}$ are not interchangeable. A node-link diagram, however, may underrepresent the edge count if the edges $x_{ij}$ and $x_{ji}$ both exist and are drawn on top of one another. Ultimately, t}here is not one "correct" way to visualize network information, and we will be using both \st{the node-link and adjacency matrix visualization} methods throughout this paper.

@@

\hh{mostly lit review plus a detailed description of the model and fitting process.}

@@

For the network $x$ and each actor $i$ in the network, the number of times that an actor $i$ gets to change its ties, $x_{ij}$, to other nodes $j \neq i$ in the network is dictated by a \emph{rate function} $\rho(x, \mathbf{z}, \boldsymbol{\alpha})$. For this paper, we assume a simple rate \st{"function"}, $\rho(x, \mathbf{z}, \boldsymbol{\alpha}) = \alpha_m$ that is constant for all actors between observations at time $t_m$ to $t_{m+1}$, \st{thus our rate function is just a rate parameter in the model}. \hh{XXX that means that the function is essentially just a rate parameter, right?} \st{XXX yes XXX}
Other modelling scenarios allow this rate to be more flexible,  e.g.\ a function that depends on the time period of observation, some actor-level covariates or some actor-level network statistics. 
\hh{How is the rate parameter different from a rate parameter?} \st{I think you meant how is a rate fn different from a rate parameter? I updated the language XXX->}%In our model with the simple rate function, 
\st{In our simple model with a rate parameter instead of a rate function,} the rate parameter determines how quickly actor $i$ gets an opportunity to change one of its ties, $x_{ij}$ in the time period from $t_{m}$ to $t_{m+1}$. The model also assumes that the actors $i$ are conditionally independent given their ties, $x_{i1}, \dots, x_{in}$ at the current network state. \st{Let $\tau_i(m)$ be the wait time until actor $i$ makes its next change.For any time point, $T$, where $t_{m} \leq T < t_{m+1}$, the waiting time to the next change opportunity by actor $i$ is exponentially distributed with expected value $\alpha_m^{-1}$. The conditional independence assumption is expressed in Equation~\ref{eq:c1}.

@@

\hh{XXX we tried to estimate the rate based on the simulations - you could include a histogram of the number of changes for the 1000 simulations in the viz part XXX}
\st{XXX I have the fitted models from the 1000 simulations (see Figure \ref{fig:distests}). Is that what you mean? XXX}

@@

\hh{shouldn't that be independence? - make the conditional independence assumption above a labelled formula (e.g. C1) and then call it here }
Because of the conditional \st{in}dependence assumptions in Equation~\ref{eq:c1}, we can consider the objective function for each node separately, since only one tie from one node is \st{allow to change} at a time. \st{The node $i$, which is the node that is chosen to change at the current time point, is called the \textit{ego} node. It has the potential to interact with all other nodes in the network, $j \neq i$. These nodes $j$, are referred to as \textit{alters}. These nodes are acted upon by the ego node, and they only act when they become the ego node at a subsequent time point.} So, for the ego node, $i$, in the current network state $x$, the objective function is then written as 
\begin{equation} \label{eq:of1}
f_i(\boldsymbol{\beta}, x) = \sum_k \beta_k s_{ik}(x, \mathbf{Z}),
\end{equation}

for $x \in \mathcal{X}$, the space of all possible directed networks with the $n$ nodes, and $\mathbf{Z}$ matrix of covariates. The vector $\boldsymbol{\beta}$ are the parameters of the model with corresponding network and covariate statistics, $s_{ik}(x, \mathbf{Z})$, for $k = 1,\dots, K$. \hh{XXX ego node isn't defined yet - the description of the charts would be a good place for it.} \st{XX I added it above the obj function equation. Is it ok there?} Given the ego node, $i$, there are $n$ possible steps for the actor $i$ to take: either one of all current ties $x_{ij} = 1$ will be destroyed, a new tie will be created, or no change will occur.

The parameters, $\boldsymbol{\beta}$, are attached to various actor-level network statistics, $s_{ik}(x)$. %\hh{'There are always' ... that seems to come from a Snijder paper? Re-phrase this to be less vague: In the current implementation of RSiena (snijder) a model has minimally two parameters...} 
According to \citet[p. 371]{snijders01}, there should be at least two parameters included in the model: $\beta_1$ for the outdegree of a node, and $\beta_2$ for the number of reciprocal ties held by a node \st{The inclusion of these effects has origin in the classical exponential random graph model (ERGM) for networks. The statistics corresponding to these effects are written in terms of the edge variables $x_{ij}$, for $i \neq j$.} In the \texttt{RSiena} software, there are over 80 possible parameters to add to the model. The formulas for the effects are provided in \citet{RSienamanual}. The parameters, $\beta_k$, in the model can be split up into two groups: first, the structural effects, whose estimation only depend on the structure of the network, like the outdegree and reciprocity parameters mentioned above. \hh{XXX move the last colored section to the front of this paragraph. That sets up the structure nicely, e.g. `In determining the covariates of a SAOM, two sources of parameters are considered: ...} \st{XXX as I'm going through and uncommenting your comments (sorry....) this one has lost meaning a little bit. Could you give me more detail? I'm not sure which section is which at this point. (sorry again...)}
The second set of effects are referred to as the actor-level or covariate effects. These covariate effects also depend on the structure of the network, and are written in terms of the tie variables $x_{ij}$, but also in terms of the covariates, $\mathbf{Z}$. A table of some possible structural and covariate effects is given in Table~\ref{tab:effects}. For a complete list of the network and covariate statistics that can currently be included in the objective function, see \citet{RSienamanual}.

@@

Using the distribution given in Equation~\ref{dist1} with mean $\mu = 0$ and scale $\sigma = 1$ as \citet{modelsSnijders} suggests \hh{XXX I'm not following - which distribution do you mean by `this' distribution? The density above is the type 1 extreme value density. I got lost at the  ``objective function $f_i(\boldsymbol{\beta}, x)$ plus a random element, $U_i(x)$"} \st{XXX I hope it is clearer now above}
is convenient because its \st{properties lead to a probability formula for} the probability that actor $i$ chooses to change its tie to actor $j$ \st{that can be written only} in terms of the objective function. Let $p_{ij}(\boldsymbol{\beta}, x)$ be the probability that actor $i$ chooses to change its tie to actor $j$. Next, we write the network $x$ in its potential future state, where the tie $x_{ij}$ has changed to $1-x_{ij}$, as $x(i \leadsto j)$. Then, the probility that the tie $x_{ij}$ changes is

@@

\hh{XXX This paragraph ends a bit abruptly - what is the future state probability used for?} \st{XX The future state probability is used within the continuous time markov chain to move through the different network states. This needs more fleshing out. Adding to the to-do list.}

\subsubsection{Continuous Time Markov Chain}

\st{XXX TO DO XXX}
